WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-02-17 article/Article.tex
add description for auto_progress
darcs-hash:20060217182403-2fc9d-0c65d4ee2e971dc17ed6471bf04501617758bff1.gz

  \item \verb$itk.auto_progress$

>>>>

  \item \verb$itk.auto_progress( b )$ is used to automatically add a progress report
to all the newly created filters. \verb$b$ must be \verb$True$ or \verb$False$. If
\verb$b$ is true, a line like
\begin{verbatim}
itkMedianImageFilterIF2IF2: 0.109990
\end{verbatim}
is displayed on the standard output. 
While prototyping, it is a convenient way for the user to know if
the execution time will be short or if he can do something more useful than waiting
for the filter to complete (like having a cup of tea).
